\input{modules/name.tex}

The name of the organization should be memorable.  According to cognitive 
psycology, the name should consist of multiple words evoking images that 
are common and which contrast to make them easier to memorize.  Ideally 
the name should also induce a sense of cognitive dissonance such that the
reader takes the time to focus on making sense of it, thus again increasing
memorability.  However, care must be taken to ensure the words and dissonance
do not evote negative emotions or ideas, such as disgust, as this would
be detrimental to the brand.  Ideally, the idea of fear or insecurity when
working with IT infrastructure or devices should evok the name of the 
organization.

For the purposes of finding the right combination of words I will use the
\href{https://github.com/globalwordnet/english-wordnet/tree/main?tab=readme-ov-file}
{Open English Wordnet}\footnote{\url{https://github.com/globalwordnet/english-wordnet/tree/main?tab=readme-ov-file}}
project english langauge dictionary along with a custom script to find adequate 
word combinations.

Additionally, we will take the algorithm described in the paper
\href{https://arxiv.org/abs/2508.18709}
{Adaptive Originality Filtering: Rejection Based Prompting and RiddleScore for Culturally Grounded Multilingual Riddle Generation}\footnote{\url{https://arxiv.org/abs/2508.18709}}
and modify for our purposes to generate a combination of three words that
serve to evoke the following:

\begin{enumerate}
    \item Ideas of security, defense, safety, protection
    \item Ideas of risk, danger, aggression, theft
    \item A ``bridge idea'' that provides the reader with a sense of curiosity and engages them to think about the name
\end{enumerate}

\subsubsection{LionDefenseThorn}

The name \emph{LionDefenseThorn} will be provided as an example.  Additionally, 
the brand name will be augmented with icons illiciting the story of 
\href{https://en.wikipedia.org/wiki/The_Lion_and_the_Mouse
}{Lion and the Mouse}\footnote{\url{https://en.wikipedia.org/wiki/The_Lion_and_the_Mouse}}.
I'm not sure how common the story is, but, if it peaques' peoples interest to
figure out what it is and how it relates to security, then it serves it's purpose.

Note that the criteria enumerated above are all met by this name.  It will 
therefore also serve to test the accuracy of our algorithm. 

